Viscous Transport in Eroding Porous Media

### 2019-07-15 docs/transport/erosion_transport.tex
added a todo
editing in transport paper

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There are zoom windows of
the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
they are taken from the last three frames of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
  tracers around the bodies. Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}
{\color{red}
In Fig.~\ref{fig:Eroding20area} (a) we
measure the area occupied by bodies 
during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
all the bodies are vanished completely.

We record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20area} (b). 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area occupied by bodies is getting smaller $U$ is getting larger.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20flowrate}, the flow rate increases exponentially 
with growth rate close to $\ln10^4$.

>>>>

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There are zoom windows of
the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
they are taken from the last three frames of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
  tracers around the bodies. Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}
{\color{red}
In Fig.~\ref{fig:Eroding20area}(a) we
measure the area occupied by bodies 
during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
all the bodies are vanished completely.

We record the flow rate $U$ quantifily in log scale
during the eroding in Fig.~\ref{fig:Eroding20area}(b). 
Since we simulate the erosion by applying fixed pressure drop 
the flow rate $U$ is small when there are many bodies in the fluid and 
when the area occupied by bodies is getting smaller $U$ is getting larger.
When all the bodies have vanished completely the flow rate $U$ is equal to 1.
In Fig.~\ref{fig:Eroding20area}(b), the flow rate increases exponentially 
with growth rate close to $\ln10^4$.
